### 2024-06-01 getting-started.qmd
20240601 - updates

players %>%
  select(-c(position:age))

@@

```{r}
subsetRows <- c(3,4)

players[c(3,4),]
players[subsetRows,]
players[which(players$position == "RB"),]
```

@@

```{r}
players[c(3,4), c(2,4)]
players[subsetRows, subsetVars]
players[which(players$position == "RB"), subsetVars]
```

@@

Merging (also called joining) merges two data objects using a shared set of variables called "keys."
The keys are the variable(s) that uniquely identify each row (i.e., they account for the levels of nesting).
In some data objects, the key might be the participant's ID (e.g., `participantID`).
However, some data objects have multiple keys.
For instance, in long form data objects, each participant may have multiple rows corresponding to multiple timepoints.
In this case, the keys are `participantID` and `timepoint`.
If a participant has multiple rows corresponding to timepoints and measures, the keys are `participantID`, `timepoint`, and `measure`.
In general, each row should have a value on each of the keys; there should be no missingness in the keys.

To merge two objects, the keys must be present in both objects.
The keys are used to merge the variables in object 1 (`x`) with the variables in object 2 (`y`).
Different merge types select different rows to merge.

>>>>

players %>%
  select(-c(name:age))

@@

```{r}
subsetRows <- c(4,5)

players[c(4,5),]
players[subsetRows,]
players[which(players$position == "RB"),]
```

@@

```{r}
players[c(4,5), c(2,4)]
players[subsetRows, subsetVars]
players[which(players$position == "RB"), subsetVars]
```

@@

Merging (also called joining) merges two data objects using a shared set of variables called "keys."
The keys are the variable(s) that uniquely identify each row (i.e., they account for the levels of nesting).
In some data objects, the key might be the player's identification number (e.g., `player_id`).
However, some data objects have multiple keys.
For instance, in long form data objects, each participant may have multiple rows corresponding to multiple seasons.
In this case, the keys may be `player_id` and `season`.
If a participant has multiple rows corresponding to seasons and games/weeks, the keys are `player_id`, `season`, and `week`.
In general, each row should have a value on each of the keys; there should be no missingness in the keys.

To merge two objects, the key(s) that will be used to match the records must be present in both objects.
The keys are used to merge the variables in object 1 (`x`) with the variables in object 2 (`y`).
Different merge types select different rows to merge.
